---
title: "svm"
author: "Chen Ning Kuan"
date: "2020年3月30日"
output: 
  html_document:
    theme: cerulean
    toc: true
    # toc_depth: 2
    number_sections: true
  # word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Make linear seperable sample

## show how to make it

Our goal is to make a hyperplane that can separate two label(y)

In this simple case we only have two feature x1 and x2 and two label

y=1 or y=-1(maybe y=1 represent boy,y=-1 represent girl)


```{r}

set.seed(2)
n = 10
a1 = rnorm(n)
a2 = 1 - a1 + 2* runif(n)
b1 = rnorm(n)
b2 = -1 - b1 - 2*runif(n)
x = rbind(matrix(cbind(a1,a2),,2),matrix(cbind(b1,b2),,2))
y <- matrix(c(rep(1,n),rep(-1,n)))
plot(x,col=ifelse(y>0,4,2),pch=".",cex=7,xlab = "x1",ylab = "x2")

#blue is+1
#red  is-1

```

## show the data we called df

```{r}

df<- cbind(x,y)
colnames(df) <- c("x1","x2","y(label)")
df
```

# Introduce svm algorithm

## step1 

$f(x)=w_0+w_1x_1+w_2x_2$

## step2 

## step3 gradient decesnt


# svm from scratch in R

## prepare step

```{r}
set.seed(2)
X<- cbind(1,x) #make design matrix
n <- nrow(X)  #number of sample
p <- ncol(X) #number of feature+1 (bias)
w_intial <- rnorm(p,0,3)
w <- w_intial
eta <- 0.001
R <- 7 #number of iteration
W <- matrix(w_intial ,nrow = R+1,ncol = p,byrow = T) #matrix put intial guess and the procedure to do gradient descent 
W
```

## indicator function

```{r}
indicator<-function(condition) ifelse(condition,1,0)
a <- 3
indicator( a<1 )
(a<4)*1


```


## part of gradient descent

```{r}
require(magrittr)
X%*%w
dim(X)

sum(   ((y*(X%*%w))<1)*1 * y * X[,1] )

sum(   ((y*(X%*%w))<1)*1 * y * X[,2] )

sum(   ((y*(X%*%w))<1)*1 * y * X[,3] )

gradient <- function(i){
  
a<- sum(   ((y*(X%*%w))<1)*1 * y * i )  
return(a)
}

apply( X,2,gradient  )

```

```{r}

w_intial[1]-eta*sum(   ((y*(X%*%w))<1)*1 * y * X[,1] )

w_intial[2]-eta*sum(   ((y*(X%*%w))<1)*1 * y * X[,2] )

w_intial[3]-eta*sum(   ((y*(X%*%w))<1)*1 * y * X[,3] )

#m=c()

#for(j in 1:p){
  
  
#m[j]<- w_intial[j]-eta*sum(   ((y*(X%*%W[1,]))<1)*1 * y * X[,j] )  
  
#}

#m
#X%*%W[1,]
```

```{r}

w_intial[1]-eta*sum(   ((y*(X%*%W[1,]))<1)*1 * y * X[,1] )
#W[,1] imply the 1th iteration

w_intial[2]-eta*sum(   ((y*(X%*%W[1,]))<1)*1 * y * X[,2] )

w_intial[3]-eta*sum(   ((y*(X%*%W[1,]))<1)*1 * y * X[,3] )
```

```{r}
eta
W

for(i in 1:R){
for(j in 1:p){
W[i+1,j]<- W[i,j]-eta*sum(((y*(X%*%W[i,]))<1)*1 * y * X[,j] )  
}
}
W
```


```{r}

svm_gradient<- function(x,eta=0.001,R=10000){
  
X<- cbind(1,x)#make design matrix
X
n <- nrow(X)  #number of sample
p <- ncol(X) #number of feature+1 (bias)
w_intial <- rnorm(p,0,1)
W <- matrix(w_intial ,nrow = R+1,ncol = p,byrow = T) #matrix put intial guess and the procedure to do gradient descent

for(i in 1:R){
  for(j in 1:p)
  {
    W[i+1,j]<- W[i,j]+eta*sum(((y*(X%*%W[i,]))<1)*1 * y * X[,j] )  
  }
  }
  
return(W)  
}

#svm_gradient(x)
#dim(svm_gradient(x))
w_answer<- svm_gradient(x)[nrow(svm_gradient(x)),]
w_answer

X%*%w_answer

y
```

```{r}
f <- function(x1,x2) w_answer[1]+w_answer[2]*x1+w_answer[3]*x2
x2 <- x1 <- seq(-10,10,length=100)
z <- outer(x1,x2,f)
contour(
  x=x1, y=x2, z=z, 
  levels=0, las=1, drawlabels=FALSE, lwd=3
)
```


```{r}
set.seed(2)
n = 100
a1 = rnorm(n)
a2 = 1 - a1 + 2* runif(n)
b1 = rnorm(n)
b2 = -1 - b1 - 2*runif(n)
x = rbind(matrix(cbind(a1,a2),,2),matrix(cbind(b1,b2),,2))
y <- matrix(c(rep(1,n),rep(-1,n)))
plot(x,col=ifelse(y>0,2,4),pch=".",cex=7,xlab = "x1",ylab = "x2")
w_answer<- svm_gradient(x)[nrow(svm_gradient(x)),]
abline(-w_answer[1]/w_answer[3],-w_answer[2]/w_answer[3])
abline(1-w_answer[1]/w_answer[3],-w_answer[2]/w_answer[3],lty=2)
abline(-1-w_answer[1]/w_answer[3],-w_answer[2]/w_answer[3],lty=2)
```

```{r}
set.seed(2)
n = 100
a1 = rnorm(n)
a2 = 1 + a1 + 2* runif(n)
b1 = rnorm(n)
b2 = -1 + b1 - 2*runif(n)
x = rbind(matrix(cbind(a1,a2),,2),matrix(cbind(b1,b2),,2))
y <- matrix(c(rep(1,n),rep(-1,n)))
plot(x,col=ifelse(y>0,2,4),pch=".",cex=7,xlab = "x1",ylab = "x2")
w_answer<- svm_gradient(x)[nrow(svm_gradient(x)),]
abline(-w_answer[1]/w_answer[3],-w_answer[2]/w_answer[3])
abline(1-w_answer[1]/w_answer[3],-w_answer[2]/w_answer[3],lty=2)
abline(-1-w_answer[1]/w_answer[3],-w_answer[2]/w_answer[3],lty=2)
```

```{r}

set.seed(2)
n = 100
a1 = rnorm(n)
a2 = 1 - a1 + 2* runif(n)
b1 = rnorm(n)
b2 = -1 + b1 - 2*runif(n)
x = rbind(matrix(cbind(a1,a2),,2),matrix(cbind(b1,b2),,2))
y <- matrix(c(rep(1,n),rep(-1,n)))
plot(x,col=ifelse(y>0,2,4),pch=".",cex=7,xlab = "x1",ylab = "x2")

```


```{r}


f <- function(x,y) x^2 - 3*y^2 + 2*x*y - 20
x <- y <- seq(-10,10,length=100)
z <- outer(x,y,f)
contour(
  x=x, y=x, z=z, 
  levels=0, las=1, drawlabels=FALSE, lwd=3
)
```

